---
title: "Tabooness Survey Results"
output: html_document
---
```{r, echo = F, message = F}
library(knitr)
source('analysis.R')

``` 
### Average Tabooness for All 21 Sentences

```{r, echo = F, message = F}
kable(words.avg, 'markdown')
``` 
### Average Tabooness when used in positive contexts

```{r, echo = F, message = F}
pos.only <- GetMeansDF(results,'Pos')
pos.mean <- mean(pos.only$mean)
kable(pos.only, 'markdown')
``` 
Average mean overall: `r pos.mean`

### Average Tabooness when used in negative contexts

```{r, echo = F, message = F}
neg.only <- GetMeansDF(results,'Neg')
neg.mean <- mean(neg.only$mean)
kable(neg.only, 'markdown')
``` 
Average mean overall: `r neg.mean`

### Average Tabooness when used in denotative contexts

```{r, echo = F, message = F}
den.only <- GetMeansDF(results,'Den')
den.mean <- mean(den.only$mean)
kable(den.only, 'markdown')
``` 
Average mean overall: `r den.mean`

### Average Tabooness for Specific words

#### Fuck
```{r, echo = F, message = F}
fuck.only <- GetMeansDF(results,'Fuck')
fuck.mean <- mean(fuck.only$mean)
kable(fuck.only, 'markdown')
``` 
Average mean overall: `r fuck.mean`

#### Shit
```{r, echo = F, message = F}
shit.only <- GetMeansDF(results,'Shit')
shit.mean <- mean(shit.only$mean)
kable(shit.only, 'markdown')
``` 
Average mean overall: `r shit.mean `

#### Bitch
```{r, echo = F, message = F}
bitch.only <- GetMeansDF(results,'Bitch')
bitch.mean <- mean(bitch.only$mean)
kable(bitch.only, 'markdown')
``` 
Average mean overall: `r bitch.mean`

#### Damn
```{r, echo = F, message = F}
damn.only <- GetMeansDF(results,'Damn')
damn.mean <- mean(damn.only$mean)
kable(damn.only, 'markdown')
``` 
Average mean overall: `r damn.mean`

#### Hell
```{r, echo = F, message = F}
hell.only <- GetMeansDF(results,'Hell')
hell.mean <- mean(fuck.only$mean)
kable(hell.only, 'markdown')
``` 
Average mean overall: `r hell.mean`

#### Gay
```{r, echo = F, message = F}
gay.only <- GetMeansDF(results,'Gay')
gay.mean <- mean(gay.only$mean)
kable(gay.only, 'markdown')
``` 
Average mean overall: `r gay.mean`

#### Pussy
```{r, echo = F, message = F}
pussy.only <- GetMeansDF(results,'Pussy')
pussy.mean <- mean(pussy.only$mean)
kable(pussy.only, 'markdown')
``` 
Average mean overall: `r pussy.mean`
